Defending Byzantine Attacks in Ensemble Federated Learning: A Reputation-based Phishing Approach

### 2021-12-22 Manuscript/FLPhish(Trans).tex
修改： introduction重审一遍 % FLPhish           scheme % FL                architecture % other robust FL   schme % Ensemble FL       architecture % FLPhish-threshold aggregation rule % FLPhish-weight    aggregation rule

\maketitle

\begin{abstract}
  With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend Byzantine attacks. In this paper, we present a reputation-based phishing scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL framework. First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence. Last, we propose two aggregation techniques with FLPhish: FLPhish-threshold and FLPhish-weight. FLPhish is tested with varying proportions of Byzantine clients and varying degrees of distribution imbalance. Extensive experiments under different situations demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

@@

\section{Introduction}
\IEEEPARstart{M}{any} Many elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the app's users. Developers get information from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy protection, making it difficult to get data directly from consumers anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data of each user, the central server in FL only needs to train its global model using their gradient model updates. FL protects each participating individual's privacy while leveraging the capabilities of the end users' computation and storage.

\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system. Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy}\cite{ref_34_VerifyNet}. Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers. Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network\cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types: A) The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. B) Another group of Byzantine-robust approaches (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in traditional FL. This architecture is flexible by supporting different types of deep learning models in each client and makes FL more flexible.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients more accurately.
  \item We propose two aggregation algorithms, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
\end{itemize}

@@

\par This system model demonstrates a variety of advantages over traditional FL architectures:
\begin{itemize}

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in traditional FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients). Different selected features in different clients are permitted as well.
  \item The overhead and latency of the communication process are significantly reduced compared to the traditional FL architecture. Transferring data is much faster than transferring gradient updates. 
  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the next section.
\end{itemize}

>>>>

\maketitle
% FLPhish           scheme
% FL                architecture
% other robust FL   schme
% Ensemble FL       architecture
% FLPhish-threshold aggregation rule
% FLPhish-weight    aggregation rule
\begin{abstract}
  With the emerging demand for personal privacy, FL is becoming a popular distributed machine learning paradigm. Nonetheless, the implementation of FL is still vulnerable to Byzantine attacks, which can bring significant hazards to the global model aggregation process, and is extremely difficult to defend. In this paper, we present a reputation-based robust-FL scheme (FLPhish) for defending Byzantine attacks under the Ensemble FL architecture. First, we design a new Ensemble FL architecture, which is compatible with different deep learning models for different clients. Second, we craft a phishing mechanism for the Ensemble FL architecture to identify Byzantine attacks. Furthermore, a reputation mechanism based on the Bayesian inference is presented to measure each client's level of confidence. Last, we propose two aggregation rules with FLPhish: FLPhish-threshold and FLPhish-weight. FLPhish is tested with different fractions of Byzantine clients and different degrees of distribution imbalance. Extensive experiments under different settings demonstrate that the proposed FLPhish achieves great efficacy in resisting Byzantine attacks in Ensemble FL.
\end{abstract}

@@

\section{Introduction}
\IEEEPARstart{M}{any} Many elements of our daily lives and society have benefited from deep learning tasks in natural language processing, computer vision, and anomaly detection. To learn complex rules, such activities necessitate a large dataset. In most cases, these huge datasets are gathered from users, such as the online shopping app users' purchase record data, patients' clinical data and etc. Developers get a large-scale data from users and utilize it to create the dataset. Nonetheless, in recent years, there has been an explosion in social concerns about personal privacy, making it difficult to get data directly from consumers anymore. Under these circumstances, each individual's data is referred to as an `Isolated Data Island'. The existence of each `Isolated Data Island' drives the development of privacy-preserving solutions like Federated Learning \cite{ref_02_FLConcept}. Google built the world's first product-level scalable mobile FL system based on TensorFlow\footnote{https://federated.withgoogle.com/}. Its FL system could be operated on thousands of mobile phones. Moreover, a team of WeBank developed an FL scheme called FATE\footnote{https://github.com/FederatedAI/FATE} for credit risk prediction. And some former researchers have also applied FL in some industrial cyber–physical Systems \cite{ref_42_FLApp, ref_43_FLApp}.

\par FL is a distributed machine learning paradigm, which allows a central server to train a global model without gaining access to each individual's private data. Instead of gathering private data of each user, the central server in FL only needs to train its global model using their gradient model updates. In each iteration of FL, the central server sends a model to each client. The client will use its own private data to update the model and sends the model gradient update back to the central server. Then the central server aggregates all the clients' updates to a global model gradient update, and updates the global model using the global model gradient update. FL protects each participating individual's privacy while leveraging the capabilities of the end users' computation and storage.

\par Since thousands of clients from different sources may participate in the training process of FL, security issues also exist in such a large-scale distributed system. Former researchers have already studied the privacy problems of FL and have proposed the corresponding schemes to enhance privacy protection in FL \cite{ref_33_privacy, ref_34_VerifyNet}. Meanwhile, FL clients may also be manipulated or poisoned by malicious attackers. Researchers call such attacks Byzantine attacks referring to the same types of attack in wireless communication network \cite{ref_35_Byzantine,ref_36_Byzantine,ref_37_Byzantine,ref_38_Byzantine,ref_40_Byzantine}. By poisoning the clients' datasets or directly manipulating the gradient updates, the incorrect gradient updates are sent by the malicious clients to the central server, which causes the central server's global updates to learn incorrect knowledge from the clients. As a result, this process renders the central server's global model obsolete. Furthermore, Byzantine attacks can be divided into two types based on the attack consequences: targeted attacks and untargeted attacks. The disturbed global model randomly delivers inaccurate predictions for the test dataset in untargeted attacks \cite{ref_04_model,ref_06_model,ref_07_data}. In targeted attacks, the global model generates labels for the testing dataset in a predetermined pattern chosen by the attackers \cite{ref_08_data,ref_09_backdoor,ref_10_backdoor,ref_11_backdoor,ref_19_backdoor}.

\par Former researchers have offered certain Byzantine-robust techniques to deal with malevolent Byzantine clients under the FL application settings \cite{ref_12_defense,ref_13_defense,ref_15_defense,ref_16_defense,ref_17_defense,ref_28_defense,ref_29_defense,ref_30_defense,ref_31_defense,ref_32_defense}. In the presence of a bounded number of malicious clients, Byzantine-robust approaches try to develop a global model with high accuracy. According to their different mechanisms, we divide Byzantine-robust approaches into two major types: A) The first (named Byzantine-Detection) is based on the creation of a Byzantine-robust aggregation rule that distinguishes questionable customers from benign clients. The server then eliminates the suspected clients' gradient updates from the aggregate process. For instance, in DRACO, each node analyzes duplicate gradients that the parameter server uses to mitigate the effects of adversarial updates \cite{ref_13_defense}. B) Another group of Byzantine-robust approaches (named Byzantine-Tolerance) aims to ensure that the aggregation process is tolerant of Byzantine clients' poisoned updates without excluding Byzantine clients like Median \cite{ref_16_defense}. The FL server sorts the values of each parameter based on Median and selects the median value of each parameter as the value to be used in global model updates. Recent research, however, suggests that current approaches are still vulnerable to Byzantine attacks \cite{ref_06_model}. Based on the above analysis, in this paper, we present a novel reputation-based phishing scheme (called FLPhish) in defending against Byzantine attacks in Ensemble FL. Our contributions are four-folds:
\begin{itemize}
  \item We design a new FL architecture, Ensemble Federated Learning (called Ensemble FL), which utilizes an unlabeled dataset to replace the gradient updates in typical FL. This architecture is flexible by supporting different types of deep learning models in each client and makes FL more flexible.
  \item We craft a `phishing' method based on Ensemble FL to detect Byzantine attacks. The `phishing' method employs the labeled dataset to detect the potential Byzantine clients in the Ensemble FL system, which preserves the security of Ensemble FL.
  \item We present a Bayesian inference-based reputation mechanism to promote FLPhish's aggregation. The reputation mechanism gives each client a reputation to measure its confidence value and identifies the clients with low reputation values as Byzantine clients, which helps FLPhish identify the Byzantine clients more accurately.
  \item We propose two aggregation rules, called FLPhish-threshold and FLPhish-weight, to aggregate the predictions of the FL clients, based on reputation mechanism, which contribute to the robustness of FLPhish. That is, FLPhish-threshold identifies the clients with low reputation values as Byzantine clients, while FLPhish-weight utilizes the reputation value of each client as its aggregation weight to participate aggregation process.
\end{itemize}

@@

\par This system model demonstrates a variety of advantages over typical FL architectures:
\begin{itemize}

  \item The selection of the global model and each client's local model is restricted to the same type of neural architecture in typical FL. Nevertheless, in our system, deploying different types of neural architectures is allowed by applying the distilled knowledge (the predictions of the unlabeled data produced by the clients). Different selected features in different clients are permitted as well.
  \item The overhead and latency of the communication process are significantly reduced compared to the typical FL architecture. Transferring data is much faster than transferring gradient updates. 
  \item The design of Ensemble FL can prevent the backdoor attack in FL. The detail of theoretical proof will be in the next section.
\end{itemize}
